Methods for Large Scale Learning to Rank

### 2014-04-14 report/Chapters/BenchmarkResults.tex
L2 regulatisation -> ridge

\begin{table}[!h]
\begin{tabular}{l|p{1.2cm}p{1.2cm}p{1.2cm}p{1.4cm}||l}
 & \rotatebox{55}{Regression + L2 regulatisation} & \rotatebox{55}{Rank\ac{SVM}-Primal} &\rotatebox{55}{Rank\ac{SVM}-Struct} & \rotatebox{55}{SmoothRank} & \rotatebox{55}{ListNet} \\
 \hline
TD2003 & 0.3297 & 0.3571 & 0.3467 & 0.3367 & 0.348 \\ 
TD2004 & 0.2832 & 0.2913 & 0.3090 & 0.3343 & 0.317 \\ 
NP2003 & 0.8025 & 0.7894 & 0.7955 & 0.7986 & 0.801 \\ 
NP2004 & 0.8040 & 0.7950 & 0.7977 & 0.8075 & 0.812 \\ 
HP2003 & 0.8216 & 0.8180 & 0.8162 & 0.8325 & 0.837 \\ 
HP2004 & 0.7188 & 0.7720 & 0.7666 & 0.8221 & 0.784 \\ 
OHSUMED & 0.4436 & 0.4504 & 0.4523 & 0.4568 & 0.441 \\ 
\# winning datasets & 2 & 2 & 1 & 3 & - \\ 
\end{tabular}
\caption{\acs{nDCG}@10 comparison of algorithms recently evaluated on LETOR 3.0 with the ListNet baselines}
\label{tbl:LETOR_recently_added}
\end{table}

>>>>

\begin{table}[!h]
\begin{tabular}{l|p{1.2cm}p{1.2cm}p{1.2cm}p{1.4cm}||l}
 & \rotatebox{55}{Ridge Regression} & \rotatebox{55}{Rank\ac{SVM}-Primal} &\rotatebox{55}{Rank\ac{SVM}-Struct} & \rotatebox{55}{SmoothRank} & \rotatebox{55}{ListNet} \\
 \hline
TD2003 & 0.3297 & 0.3571 & 0.3467 & 0.3367 & 0.348 \\ 
TD2004 & 0.2832 & 0.2913 & 0.3090 & 0.3343 & 0.317 \\ 
NP2003 & 0.8025 & 0.7894 & 0.7955 & 0.7986 & 0.801 \\ 
NP2004 & 0.8040 & 0.7950 & 0.7977 & 0.8075 & 0.812 \\ 
HP2003 & 0.8216 & 0.8180 & 0.8162 & 0.8325 & 0.837 \\ 
HP2004 & 0.7188 & 0.7720 & 0.7666 & 0.8221 & 0.784 \\ 
OHSUMED & 0.4436 & 0.4504 & 0.4523 & 0.4568 & 0.441 \\ 
\# winning datasets & 2 & 2 & 1 & 3 & - \\ 
\end{tabular}
\caption{\acs{nDCG}@10 comparison of algorithms recently evaluated on LETOR 3.0 with the ListNet baselines}
\label{tbl:LETOR_recently_added}
\end{table}
